### 2014-07-17 doc/thesis/cases.tex
Finishing to port the current typing of the Lua Standard Libraries to its description file

\subsection{Coroutine manipulation}

\begin{enumerate}
\item coroutine.create (f) :
$(\TopStar \rightarrow \TopStar) \times \TopStar \rightarrow Thread \times \NilStar$
\item coroutine.resume (co [, val1, ···]) :
$Thread \times
\TopStar \rightarrow
(\True \times \AnyStar) \cup
(\False \times \String \times \NilStar)$
\item coroutine.running () :
$\TopStar \rightarrow Thread \times \Boolean \times \NilStar$
\item coroutine.status (co) :
$Thread \times \TopStar \rightarrow \String \times \NilStar$
\item coroutine.wrap (f) :
$(\TopStar \rightarrow \TopStar) \times
\TopStar \rightarrow
(\TopStar \rightarrow \TopStar) \times
\NilStar$ 
\item coroutine.yield (···) :
$\TopStar \rightarrow \NilStar$
\end{enumerate}

@@

\begin{enumerate}
\item require (modname) :
$\String \times \TopStar \rightarrow \{\Any:\Any\} \times \NilStar$
\\
The function \textbf{require} returns exactly the same value that is
returned by loading \textbf{modname}.
However, if the returned value is $\Nil$, this value is
converted to $\True$.
\item package.config : $\String$
\item package.cpath : $\String$
\item package.loaded : $\{\String:\{\Any:\Any\}\}$
\item package.loadlib (libname, funcname) :
$\String \times
\String \times
\TopStar \rightarrow
(\True \times \NilStar) \cup
(\Nil \times \String \times \NilStar)$
\item package.path : $\String$
\item package.preload : $\{\String:\{\Any:\Any\}\}$
\item package.searchers : $\{\Number:\TopStar \rightarrow \TopStar\}$
\item package.searchpath (name, path [, sep [, rep]]) :
$\String \times
\String \times
(\String \cup \Nil) \times
(\String \cup \Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \String \times \NilStar)$
\end{enumerate}

@@

\subsection{Input and Output facilities}

\begin{enumerate}
\item io.close ([file]) :
$(Userdata \cup \Nil) \times
\TopStar \rightarrow
(\Boolean \times \NilStar) \cup
(\Nil \times \String \times \NilStar) \cup
((\True \cup \Nil) \times \String \times \Number \times \NilStar)$
\\
Returns $((\True \cup \Nil) \times \String \times \Number \times \NilStar)$
when the file handle was created with \textbf{io.popen}.
\item io.flush () :
$\TopStar \rightarrow \Boolean \times \NilStar$
\item io.input ([file]) :
$(\String \cup Userdata \cup \Nil) \times
\TopStar \rightarrow
Userdata \times
\NilStar$
\item io.lines ([filename ···]) :
$(\String \cup Userdata \cup \Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \NilStar)$
\\
In fact, this function returns an iterator. Need to check the return type.
\item io.open (filename [, mode]) :
$\String \times
(``r" \cup ``w" \cup ``a" \cup
``r+" \cup ``w+" \cup ``a+" \cup
``rb" \cup ``wb" \cup ``ab" \cup
``r+b" \cup ``w+b" \cup ``a+b" \cup
\Nil) \times
\TopStar \rightarrow
(Userdata \times \NilStar) \cup
(\Nil \times \String \times \Number \times \NilStar)$
\item io.output ([file]) :
$(\String \cup Userdata \cup \Nil) \times
\TopStar \rightarrow
Userdata \times
\NilStar$
\item io.popen (prog [, mode]) :
$\String \times
(``r" \cup ``w" \cup \Nil) \times
\TopStar \rightarrow
(Userdata \times \NilStar) \cup
(\Nil \times \String \times \Number \times \NilStar)$
\item io.read (···) :
$(``*n" \cup ``*a" \cup ``*l" \cup ``*L" \cup \Number){*} \rightarrow
(\String \cup \Number){*}
$
\item io.tmpfile () :
$\TopStar \rightarrow Userdata \times \NilStar$
\item io.type (obj) :
$\Top \times \TopStar \rightarrow (``file" \cup ``closed\;file" \cup \Nil) \times \NilStar$
\item io.write (···) :
$(\String \cup \Number){*} \rightarrow
(Userdata \times \NilStar) \cup
(\Nil \times \String \times \Number \times \NilStar)$
\item file:close () : ?
\item file:flush () : ?
\item file:lines (···) : ?
\item file:read (···) : ?
\item file:seek ([whence [, offset]]) : ?
\item file:setvbuf (mode [, size]) : ?
\item file:write (···) : ?
\end{enumerate}

\subsection{Operating System facilities}

\begin{enumerate}
\item os.clock () :
$\TopStar \rightarrow \Number \times \NilStar$
\item os.date ([format [, time]]) :
$(\String \cup \Nil) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\{``year":\Number,\;
   ``month":\Number,\;
   ``day":\Number,\;
   ``hour":\Number,\;
   ``min":\Number,\;
   ``sec":\Number,\;
   ``wday":\Number,\;
   ``yday":\Number,\;
   ``isdst":\Boolean \} \times \NilStar)$
\\
Returns a table when \textbf{format} contains ``\textbf{*t}''.
\item os.difftime (t2, t1) :
$\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\\
Returns \textbf{t2} when \textbf{t1} is $\Nil$.
\item os.execute ([command]) :
$(\String \cup \Nil) \times
\TopStar \rightarrow
(\Boolean \times \NilStar) \cup
((\True \cup \Nil) \times \String \times \Number \times \NilStar)$
\\
Returns just a Boolean when \textbf{command} is $\Nil$.
This Boolean means whether there is a shell available.
Returns $\True \times \String \times \Number \times \NilStar$ when
\textbf{command} terminated successfully.
Returns $\Nil \times \String \times \Number \times \NilStar$ when
\textbf{command} did not terminate sucessfully.
\item os.exit ([code [, close]]) :
$(\Number \cup \Boolean \cup \Nil) \times
\Top \times
\TopStar \rightarrow
\NilStar$
\item os.getenv (varname) :
$\String \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \NilStar)$
\item os.remove (filename) :
$\String \times
\TopStar \rightarrow
(\True \times \NilStar) \cup
(\Nil \times \String \times \Number \NilStar)$
\item os.rename (oldname, newname) :
$\String \times
\String \times
\TopStar \rightarrow
(\True \times \NilStar) \cup
(\Nil \times \String \times \Number \NilStar)$
\item os.setlocale (locale [, category]) :
$(\String \cup \Nil) \times
(``all" \cup
``collate" \cup
``ctype" \cup
``monetary" \cup
``numeric" \cup
``time" \cup
\Nil) \times
\TopStar \rightarrow
(\String \times \NilStar) \cup
(\Nil \times \NilStar)$
\item os.time ([table]) :
$(\{``year":\Number,\;
   ``month":\Number,\;
   ``day":\Number,\;
   ``hour":(\Number \cup \Nil),\;
   ``min":(\Number \cup \Nil),\;
   ``sec":(\Number \cup \Nil),\;
   ``wday":(\Number \cup \Nil),\;
   ``yday":(\Number \cup \Nil),\;
   ``isdst":(\Boolean \cup \Nil) \} \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item os.tmpname () :
$\TopStar \rightarrow \String \times \NilStar$
\end{enumerate}

\subsection{The debug library}

>>>>

\subsection{Coroutine Manipulation}

\begin{enumerate}
\item coroutine.create (f) :
\begin{verbatim}
((any*) -> (any*)) -> (any)
\end{verbatim}
Category 3.
\item coroutine.resume (co [, val1, ···]) :
\begin{verbatim}
(any, any*) -> (true, any*) | (false, string)
\end{verbatim}
Category 3.
\item coroutine.running () :
\begin{verbatim}
() -> (any, boolean)
\end{verbatim}
Category 3.
\item coroutine.status (co) :
\begin{verbatim}
(any) -> ("running"|"suspended"|"normal"|"dead")
\end{verbatim}
Category 3.
\item coroutine.wrap (f) :
\begin{verbatim}
((any*) -> (true, any*) | (false, string)) ->
((any*) -> (true, any*) | (false, string))
\end{verbatim}
Category 3.
\item coroutine.yield (···) :
\begin{verbatim}
(any*) -> ()
\end{verbatim}
Category 1?
\end{enumerate}

@@

\begin{enumerate}
\item require (modname) :
\begin{verbatim}
(string) -> ({any:any})
\end{verbatim}
Category 1.
\\
The function \textbf{require} returns exactly the same value that is
returned by loading \textbf{modname}.
However, if the returned value is $\Nil$, this value is
converted to $\True$.
This function is a primitive in the type system.
\item package.config :
\begin{verbatim}
string
\end{verbatim}
Category 1.
\item package.cpath :
\begin{verbatim}
string
\end{verbatim}
Category 1.
\item package.loaded :
\begin{verbatim}
{string:{any:any}}
\end{verbatim}
Category 2?
\item package.loadlib (libname, funcname) :
\begin{verbatim}
(string, string) -> (true)?
\end{verbatim}
Category 1?
\item package.path :
\begin{verbatim}
string
\end{verbatim}
Category 1.
\item package.preload :
\begin{verbatim}
{string:{any:any}}
\end{verbatim}
Category 2?
\item package.searchers :
\begin{verbatim}
{(any*) -> (any*)}
\end{verbatim}
Category 2?
\item package.searchpath (name, path [, sep [, rep]]) :
\begin{verbatim}
(string, string, string?, string?) -> (string)?
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
(string, string) |
(string, string, string) |
(string, string, string, string?) -> (string)?
\end{verbatim}
\end{enumerate}

@@

\subsection{Input and Output Facilities}

\begin{enumerate}
\item io.close ([file]) :
\begin{verbatim}
(any?) -> (boolean) | (nil, string) | (true?, string, number)
\end{verbatim}
Category 1?
\\
Returns \texttt{(true?, string, number)} when the file handle
was created with \textbf{io.popen}.
The parameter \textbf{file} is a \textit{userdata} and I need
to fix that on the type system.
\item io.flush () :
\begin{verbatim}
() -> (boolean)
\end{verbatim}
Category 1.
\item io.input ([file]) :
\begin{verbatim}
(string|any|nil) -> (any)
\end{verbatim}
Category 1?
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item io.lines ([filename ···]) :
\begin{verbatim}
(string|any|nil) -> ((any*) -> (any*))
\end{verbatim}
Category 1?
\\
In fact, this function returns an iterator. Need to check the return type.
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item io.open (filename [, mode]) :
\begin{verbatim}
(string,
"r"|"w"|"a"|"r+"|"w+"|"a+"|"rb"|"wb"|"ab"|"r+b"|"w+b"|"w+b"|nil) ->
(any) | (nil, string, number)
\end{verbatim}
Category 1?
\\
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item io.output ([file]) :
\begin{verbatim}
(string|any|nil) -> (any)
\end{verbatim}
Category 1?
\\
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item io.popen (prog [, mode]) :
\begin{verbatim}
(string, "r"|"w"|nil) -> (any) | (nil, string, number)
\end{verbatim}
Category 1?
\\
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item io.read (···) :
\begin{verbatim}
("*n"|"*a"|"*l"|"*L"|number*) -> (string|number*)
\end{verbatim}
Category 1.
\item io.tmpfile () :
\begin{verbatim}
() -> (any)
\end{verbatim}
Category 1?
\\
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item io.type (obj) :
\begin{verbatim}
(value) -> ("file"|"closed file"|nil)
\end{verbatim}
Category 1.
\item io.write (···) :
\begin{verbatim}
(string|number*) -> (any) | (nil, string, number)
\end{verbatim}
Category 1?
\\
Here the type \texttt{any} refers to a \textit{userdata} and
I need to fix that on the type system.
\item file:close () : ?
\item file:flush () : ?
\item file:lines (···) : ?
\item file:read (···) : ?
\item file:seek ([whence [, offset]]) : ?
\item file:setvbuf (mode [, size]) : ?
\item file:write (···) : ?
\end{enumerate}

\subsection{Operating System Facilities}

\begin{enumerate}
\item os.clock () :
\begin{verbatim}
() -> (number)
\end{verbatim}
Category 1.
\item os.date ([format [, time]]) :
\begin{verbatim}
(string?, number?) -> (string) |
                      ({"year":number, "month":number, "day":number,
                        "hour":number, "min":number, "sec":number,
                        "wday":number, "yday":number, "isdst":boolean})
\end{verbatim}
Category 1.
\\
Returns a table when \textbf{format} contains ``\textbf{*t}''.
I guess the proper type should be:
\begin{verbatim}
() | (string) | (string, number?) -> (string) |
                      ({"year":number, "month":number, "day":number,
                        "hour":number, "min":number, "sec":number,
                        "wday":number, "yday":number, "isdst":boolean})
\end{verbatim}
\item os.difftime (t2, t1) :
\begin{verbatim}
(number, number?) -> (number)
\end{verbatim}
Category 1.
\\
Returns \textbf{t2} when \textbf{t1} is $\Nil$.
\item os.execute ([command]) :
\begin{verbatim}
(string?) -> (boolean) | (true?, string, number)
\end{verbatim}
Category 3.
\\
Returns just a Boolean when \textbf{command} is $\Nil$.
This Boolean means whether there is a shell available.
Returns \texttt{(true, string, number)} when
\textbf{command} terminated successfully.
Returns \texttt{(nil, string, number)} when
\textbf{command} did not terminate successfully.
\item os.exit ([code [, close]]) :
\begin{verbatim}
(boolean|number?, value?) -> ()
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
() | (boolean|number) | (boolean|number, value?) -> ()
\end{verbatim}
\item os.getenv (varname) :
\begin{verbatim}
(string) -> (string)
\end{verbatim}
Category 1.
\item os.remove (filename) :
\begin{verbatim}
(string) -> (true) | (nil, string, number)
\end{verbatim}
Category 1.
\item os.rename (oldname, newname) :
\begin{verbatim}
(string) -> (true) | (nil, string, number)
\end{verbatim}
Category 1.
\item os.setlocale (locale [, category]) :
\begin{verbatim}
(string?, "all"|"collate"|"ctype"|"monetary"|"numeric"|"time"|nil) ->
(string) | (nil)
\end{verbatim}
Category 3?
\\
The return type depends on the input type:
\begin{verbatim}
() -> (string)
(string, "all"|"collate"|"ctype"|"monetary"|"numeric"|"time"|nil) ->
(string) | (nil)
\end{verbatim}
\item os.time ([table]) :
\begin{verbatim}
({"year":number, "month":number, "day":number,
  "hour":number?, "min":number?, "sec":number?,
  "wday":number?, "yday":number?, "isdst":boolean?}?) -> (number)
\end{verbatim}
Category 1.
\item os.tmpname () :
\begin{verbatim}
() -> (string)
\end{verbatim}
Category 1.
\end{enumerate}

\subsection{The Debug Library}
